### 2017-06-15 manuscript/manuscript.Rmd
Fill YAML info

---
title             : "Curating Research Assets in Behavioral Sciences: A tutorial on the Git version control system"
shorttitle        : "Curating Research Assets in Behavioral Sciences"

author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: 406 Schermerhorn Hall, 1190 Amsterdam Avenue MC 5501, New York, NY 10027
    email: mv2521@columbia.edu
  - name          : "James P. Curley"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Columbia University"
author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

@@

abstract: >
  Enter abstract here (note the indentation, if you start a new paragraph).

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library(knitr)  # Make sure that knit directory is project root
library(papaja)
library(tidyverse)
```

>>>>

---
title             : "Curating Research Assets in Behavioral Sciences: A Tutorial on the Git Version Control System"
shorttitle        : "Curating Research Assets in Behavioral Sciences"

author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: 406 Schermerhorn Hall, 1190 Amsterdam Avenue MC 5501, New York, NY 10027
    email: mv2521@columbia.edu
  - name          : "James P. Curley"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Columbia University, New York, USA"
author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

@@

abstract: >
  Recent calls for improving the reproducibility of research products in behavioral sciences have called for increased attention to the way in which researchers curate, collaborate, and share their research assets, but have failed to provide practical instructions on how to do so. In this tutorial paper, we explain how version control systems, such as the popular Git program, are especially suitable for the challenges to reproducibility faced by behavioral science regarding research asset curating, sharing, and collaborating. We then present a complete tutorial on how to use Git from the computer's command line, and with the popular graphical interface contained in the R Studio development environment. Git is easy to learn, presents an elegant solution to problems related to curating research assets, facilitates multi-site collaboration and productivity (by allowing multiple collaborators to work on the same source simultaneously) and can be implemented on common workflows with minimal extra effort. Git may also offer a suitable solution to transparent data (and material) sharing through popular online services, such as GitHub and Open Science Framework.

keywords          : "reproducibility; open science; version control; git; research methods"
wordcount         : "X"
bibliography      : ["references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "doc, 12pt, draftfirst"  # man / jou / doc
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library(knitr)  # Make sure that knit directory is project root
opts_chunk$set(
    fig.align = "center"
)
library(papaja)
library(tidyverse)
```
